### 2024-07-04 parts/starfree.tex
test

Let us recall that a language $L$ is \intro(language){aperiodic} whenever it is
recognized by an \kl(monoid){aperiodic} finite monoid, which turns out to be
equivalent to the following characterisation among regular languages: for all
$u,v,w$, there exists $n \in \Nat$, $u v^n w \in L$ if and only if $u v^{n+1} w
\in L$. As a consequence of this characterization, a language $L$ is aperiodic
if and only if its indicator function $\ind{L}$ is \kl{ultimately polynomial}.
This was already observed in \cite[\textbf{statement?}]{CDTL23}, and reproven
in \cite[\textbf{statement?}]{DOUE23}, but we include a proof hereafter for
readability and didactic purposes.

@@

>>>>

Let us recall that a language $L$ is \intro(language){aperiodic} whenever it is
recognized by an \kl(monoid){aperiodic} finite monoid, which turns out to be
equivalent to the following characterisation among regular languages: for all
$u,v,w$, there exists $n \in \Nat$, $u v^n w \in L$ if and only if $u v^{n+1} w
\in L$. As a consequence of this characterization, a language $L$ is aperiodic
if and only if its indicator function $\ind{L}$ is \kl{ultimately polynomial}.
This was already observed in \cite[Claim V.6]{CDTL23}, and reproven in
\cite[Claim 7.45, Lemma 7.53]{DOUE23}. We include a self-contained proof
hereafter for readability and didactic purposes.

@@

\textbf{TODO: prove the following conjecture to conclude on polynomials in general
and not just Z coefficients.}
\begin{conjecture}
    Let $\vec{X}$ be a vector of variables, and $P \in \Rel[\vec{X}]$ be a
    polynomial. The following properties are decidable
    \begin{itemize}
        \item Is $P$ \kl{represented} by a \kl{$\Rel$-polyregular function}?
        \item Is $P$ \kl{represented} by a \kl{$\Nat$-polyregular function}?
    \end{itemize}
\end{conjecture}
